Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions in a laboratory study

### 2024-10-31 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x paper omega added

---
title: "Through the eyes of the teacher - Multimodal exploration of expertise differences
  in the perception of classroom disruptions in a laboratory study"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

############## Prevalence Rating #########################

sri.preva.table <-
  sri %>%
  group_by(ID) %>%
  summarise(
    N = n(),
    "M" = round(mean(prevalence_rating), digits = 2),
    "SD" = round(sd(prevalence_rating), digits = 2),
    "Min" = min(prevalence_rating),
    "Max" = max(prevalence_rating)
  )

# insert a table into HTML
knitr::kable(sri.preva.table,
             caption = "Prevalence rating")

#### with event 
sri.preva.event.table <-
  sri %>%
  group_by(ID, event) %>%
  summarise(
    N = n(),
    "M" = round(mean(prevalence_rating), digits = 2),
    "SD" = round(sd(prevalence_rating), digits = 2),
    "Min" = min(prevalence_rating),
    "Max" = max(prevalence_rating)
  )

# insert a table into HTML
knitr::kable(sri.preva.event.table,
             caption = "Prevalence rating with events")

# create a new data frame with rating
sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))

# plotting prevalence rating for groups
preva_group_plot <- 
  sri_preva %>% 
  mutate(ID = factor(ID,
                     levels = c("Novice",
                                "Expert"
                                )
                     )
         ) %>% 
  ggplot(mapping = aes(x = ID,
                       y = prevalence_rating)) +
  geom_boxplot(mapping = aes(fill = ID),
               outlier.shape = NA) +
  geom_point(size = 1,
             alpha = 0.4,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  scale_x_discrete(limits = c("Novice", "Expert")) +
  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
  labs(x = "",
       y = "Prevalence Rating") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("How widespread is this event in the classroom?") +
  theme_cowplot()

preva_group_plot

@@

#### t-Test & effect size "Prevalence rating"
```{r sri_pr_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Prevalence Rating 
# t-test for expertise differences
t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
       y = sri$prevalence_rating[sri$ID == "Novice"],
       var.equal = TRUE)

# Prevalence Rating 
# effect size for expertise differences
d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
                      y = sri$prevalence_rating[sri$ID == "Novice"],
                      na.rm = TRUE)

round(d_sri_preva, 2)

>>>>

---
title: "Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions in a laboratory study"
output: 
  pdf_document:
    toc: true           # Add a table of contents
    number_sections: true
    latex_engine: xelatex  # Specify LaTeX engine if needed
    keep_tex: true      # Keep .tex file for debugging or customization
---

@@

# ```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# 
# ############## Prevalence Rating #########################
# 
# sri.preva.table <-
#   sri %>%
#   group_by(ID) %>%
#   summarise(
#     N = n(),
#     "M" = round(mean(prevalence_rating), digits = 2),
#     "SD" = round(sd(prevalence_rating), digits = 2),
#     "Min" = min(prevalence_rating),
#     "Max" = max(prevalence_rating)
#   )
# 
# # insert a table into HTML
# knitr::kable(sri.preva.table,
#              caption = "Prevalence rating")
# 
# #### with event 
# sri.preva.event.table <-
#   sri %>%
#   group_by(ID, event) %>%
#   summarise(
#     N = n(),
#     "M" = round(mean(prevalence_rating), digits = 2),
#     "SD" = round(sd(prevalence_rating), digits = 2),
#     "Min" = min(prevalence_rating),
#     "Max" = max(prevalence_rating)
#   )
# 
# # insert a table into HTML
# knitr::kable(sri.preva.event.table,
#              caption = "Prevalence rating with events")
# 
# # create a new data frame with rating
# sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
# 
# # plotting prevalence rating for groups
# preva_group_plot <- 
#   sri_preva %>% 
#   mutate(ID = factor(ID,
#                      levels = c("Novice",
#                                 "Expert"
#                                 )
#                      )
#          ) %>% 
#   ggplot(mapping = aes(x = ID,
#                        y = prevalence_rating)) +
#   geom_boxplot(mapping = aes(fill = ID),
#                outlier.shape = NA) +
#   geom_point(size = 1,
#              alpha = 0.4,
#              position = position_jitter(seed = 1,
#                                         width = 0.1,
#                                         height = 0.1)) +
#   scale_x_discrete(limits = c("Novice", "Expert")) +
#   scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
#   labs(x = "",
#        y = "Prevalence Rating") + 
#   scale_fill_brewer(palette  = "RdBu") +  
#   ggtitle("How widespread is this event in the classroom?") +
#   theme_cowplot()
# 
# preva_group_plot
# 
# ```

#### t-Test & effect size "Prevalence rating"
# ```{r sri_pr_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# 
# #################### T-TEST & EFFECT SIZE ############
# 
# # Prevalence Rating 
# # t-test for expertise differences
# t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
#        y = sri$prevalence_rating[sri$ID == "Novice"],
#        var.equal = TRUE)
# 
# # Prevalence Rating 
# # effect size for expertise differences
# d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
#                       y = sri$prevalence_rating[sri$ID == "Novice"],
#                       na.rm = TRUE)
# 
# round(d_sri_preva, 2)
# 
# ```

### Internal consistency (Omega) for disruption and confidence appraisal
```{r sri_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Select the relevant columns (e.g., Disruption Appraisal and Confidence Appraisal)
sri <-
  excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201),
    !disruption_appraisal == -100,
    !confidence_appraisal == -100,
    !disruption_appraisal == -99,
    !confidence_appraisal == -99,
    !disruption_appraisal == -88,
    !confidence_appraisal == -88,
    !prevalence_rating == -100,
    !prevalence_rating == -99,
    !prevalence_rating == -88
    )

# change long to wide format
sri_wide <- sri %>%
  pivot_wider(names_from = event, 
              values_from = c(disruption_appraisal, confidence_appraisal, prevalence_rating))

### DISRUPTIONS APPRAISAL

# create new data frame with only disruption items
sri_wide_disrup <- sri_wide %>%
  dplyr::select(starts_with("disruption_appraisal")) %>% 
  drop_na()

# calculate omega with omega() function  
omega_disrup <- omega(sri_wide_disrup)

# display the results 
print(omega_disrup)

### CONFIDENCE APPRAISAL

# create new data frame with only confidence items
sri_wide_confi <- sri_wide %>%
  dplyr::select(starts_with("confidence_appraisal")) %>% 
  drop_na()

# calculate omega with omega() function  
omega_confi <- omega(sri_wide_confi)

# display the results 
print(omega_confi)

@@

### Prevalence Rating as manipulation check
```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# 
# ############## Prevalence Rating as manipulation check #########################
# 
# sri.preva.table <-
#   sri %>%
#   group_by(ID) %>%
#   summarise(
#     N = n(),
#     "M" = round(mean(prevalence_rating), digits = 2),
#     "SD" = round(sd(prevalence_rating), digits = 2),
#     "Min" = min(prevalence_rating),
#     "Max" = max(prevalence_rating)
#   )
# 
# # insert a table into HTML
# knitr::kable(sri.preva.table,
#              caption = "Prevalence rating")
# 
# #### with event 
# sri.preva.event.table <-
#   sri %>%
#   group_by(ID, event) %>%
#   summarise(
#     N = n(),
#     "M" = round(mean(prevalence_rating), digits = 2),
#     "SD" = round(sd(prevalence_rating), digits = 2),
#     "Min" = min(prevalence_rating),
#     "Max" = max(prevalence_rating)
#   )
# 
# # insert a table into HTML
# knitr::kable(sri.preva.event.table,
#              caption = "Prevalence rating with events")
# 
# # create a new data frame with rating
# sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))
# 
# # plotting prevalence rating for groups
# preva_group_plot <- 
#   sri_preva %>% 
#   mutate(ID = factor(ID,
#                      levels = c("Novice",
#                                 "Expert"
#                                 )
#                      )
#          ) %>% 
#   ggplot(mapping = aes(x = ID,
#                        y = prevalence_rating)) +
#   geom_boxplot(mapping = aes(fill = ID),
#                outlier.shape = NA) +
#   geom_point(size = 1,
#              alpha = 0.4,
#              position = position_jitter(seed = 1,
#                                         width = 0.1,
#                                         height = 0.1)) +
#   scale_x_discrete(limits = c("Novice", "Expert")) +
#   scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
#   labs(x = "",
#        y = "Prevalence Rating") + 
#   scale_fill_brewer(palette  = "RdBu") +  
#   ggtitle("How widespread is this event in the classroom?") +
#   theme_cowplot()
# 
# preva_group_plot
